### 2019-02-12 2-Chapters/3-Chapter/chapter3.tex
Fix #11

\begin{listing}[H]
\begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python}
from SMPyBandits.Arms import Bernoulli
arms = [Bernoulli(0.1), Bernoulli(0.9)]

@@

\begin{listing}[H]
% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
\inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{Python}{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
\caption{Small example of \texttt{main.py} file}
\label{lst:3:main}
\end{listing}

@@

\begin{listing}[H]
% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
\inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{Python}{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
\caption{Small example of \texttt{configuration.py} file}
\label{lst:3:configuration}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}
from SMPyBandits.Arms import Bernoulli
arms = [Bernoulli(0.1), Bernoulli(0.9)]

@@

\begin{listing}[H]
% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
\inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
\caption{Small example of \texttt{main.py} file}
\label{lst:3:main}
\end{listing}

@@

\begin{listing}[H]
% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
\inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
\caption{Small example of \texttt{configuration.py} file}
\label{lst:3:configuration}
\end{listing}
